\sysfull

### 2018-08-05 paper/asplos19/systemdescription.tex
update the system overview fig

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overview.pdf}
	\caption{\sys top-level view. \sys core innovation is \emph{Adaptive Task Scheduler}. The scheduler to work requires \emph{Virtual Memory Manager}, another \sys's innovation. \note{Replace the figure with a better block diagram}}
	\label{fig:system_overview}
\end{figure}
%
\sys is a new programming and execution model for intermittent computing on energy-harvesting devices. \sys addresses the challenges outlined in Section~\ref{sec:background} to make task-based intermittent programs {\em programmable}, {\em efficient} and {\em portable}. \sys accomplishes this goal with a constellation of a new programming model and runtime software system support, that supports dynamically adaptive task-based execution. Fig.~\ref{fig:system_overview} shows an overview of \sys.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/system_overview.pdf}
	\caption{\sys top-level view. \sys core innovation are \emph{Adaptive Task Scheduler (TA)} and \emph{Virtual Memory Manager (VMM)}. (PM) stands for Phyical Memory, (App) for applicaiton, and (Tx) for Task.
	\label{fig:system_overview}
\end{figure}
%
\sys is a new programming and execution model for intermittent computing on energy-harvesting devices. \sys addresses the challenges outlined in Section~\ref{sec:background} to make task-based intermittent programs {\em programmable}, {\em efficient} and {\em portable}. \sys accomplishes this goal with a constellation of a new programming model and runtime software system support, that supports dynamically adaptive task-based execution. Fig.~\ref{fig:system_overview} shows an overview of \sys.
